--- 
title: "GI Surgical Oncology"
#author: "Jonathan C Salo MD"
#date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [zotero.bib]
biblio-style: apalike
link-citations: yes
description: "Orientation Manual for GI Surgical Oncology Service"
apple-touch-icon: "images/icon120.png"
apple-touch-icon-size: 120
favicon: "images/favicon.io"
url: https://github.com/gisurgonc/orientation
---


```{r eval=FALSE, echo=F}
install.packages("bookdown")
# or the development version
 #devtools::install_github("rstudio/bookdown")
```


```{r include=FALSE,echo=F}
# automatically create a bib database for R packages
#knitr::write_bib(c(
#  .packages(), 'bookdown', 'knitr', 'rmarkdown'
#), 'packages.bib')

# (PART\*) Inpatient {-}



```
# Overview {#Intro}

## Absences

Please notify Dr Hill, Dr Salo and Dr Squires before the beginning of the rotation if you will be away during the month. This includes vacations, meetings, interview trips, and other absences.

## Communication

Please use Haiku for messaging service attendings rather than SMS. Please check our status prior to messaging nights and weekends. If we are listed as unavailable, please contact *GI Surg Onc Attending LCI CMC*.


## Medical Records

Completing medical records in a timely fashion is critical for patient safety, billing, and compliance. Timeliness also demonstrates an understanding of how the world of surgery for which residents are being prepared functions.

## Operative Logs

Completion of operative logs is critical for board certification of the individual resident but also has implications for the appropriate assignment of residents to surgical rotations AND impacts the ability of the residency to maintain accreditation and recruit resident candidates. Residents who find it difficult to find time to maintain operative logs may find themselves excused from the operating room to complete them. Residents are expected to complete operative logs within two weeks of the end of the rotation.

## Case Assignment

The senior resident will be expected to make case assignments for junior residents and students. It in not necessary split the month by attending - splitting by case is acceptable as well. We also expect that both residents know all the patients rather than just for one attending. This helps with nursing questions, etc.

## Clinic

Clinic is an important part of a surgeon's education, where decisions are made regarding diagnostic workup, patient evaluation, and treatment planning. The expectation is that all residents on the service attend clinic once per week.

## Work Hours

If the service workload jeopardizes your ability to abide by the work hour restrictions, you must notify an attending so that arrangements can be made. The service attendings are committed to abiding by work hour restrictions. 



